### 2017-03-19 papers.tex
papers.tex: Fix remaining uncovered page numbers

\addtrack{Magpie track}{Who Said Money Can't Buy...}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{3cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{1cm}
	{}
\addpaper
	{Grant proposal: Monetary policy of sparkly things}
	{Pete, Luna, and Stefan Muller}
	{}
	{SIGBOVIK_2017_paper_62}
	{0cm}
	{}

@@

\addtrack{Dog track}{Nonstandard ML}
\addpaper
	{Batch normalization for improved DNN performance, my ass}
	{Joshua A.\ Wise}
	{}
	{SIGBOVIK_2017_paper_32}
	{1cm}
	{}
\addpaper
	{Colonel density estimation}
	{Harish Krishna \textit{et al.}}
	{}
	{SIGBOVIK_2017_paper_67}
	{1cm}
	{}
\addpaper
	{Degenerative adversarial networks}
	{Raphael Gontijo Lopes and Diptodip Deb}
	{}
	{SIGBOVIK_2017_paper_74}
	{1cm}
	{}
\addpaper
	{Stopping GAN violence: Generative unadversarial networks}
	{Samuel Albanie, S\'ebastien Ehrhardt, and Jo\~ao Henriques}
	{}
	{SIGBOVIK_2017_paper_13}
	{0cm}
	{}

@@

\addtrack{Groundhog track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{0cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad and\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{3cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{3cm}
	{}
\addreview{SIGBOVIK_2017_review-23}{0cm}

>>>>

\addtrack{Magpie track}{Who Said Money Can't Buy...}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{3cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{1cm}
	{}
\addpaper
	{Grant proposal: Monetary policy of sparkly things}
	{Pete, Luna, and Stefan Muller}
	{}
	{SIGBOVIK_2017_paper_62}
	{1cm}
	{}

@@

\addtrack{Dog track}{Nonstandard ML}
\addpaper
	{Batch normalization for improved DNN performance, my ass}
	{Joshua A.\ Wise}
	{}
	{SIGBOVIK_2017_paper_32}
	{1cm}
	{}
\addpaper
	{Colonel density estimation}
	{Harish Krishna \textit{et al.}}
	{}
	{SIGBOVIK_2017_paper_67}
	{1cm}
	{}
\addpaper
	{Degenerative adversarial networks}
	{Raphael Gontijo Lopes and Diptodip Deb}
	{}
	{SIGBOVIK_2017_paper_74}
	{1cm}
	{}
\addpaper
	{Stopping GAN violence: Generative unadversarial networks}
	{Samuel Albanie, S\'ebastien Ehrhardt, and Jo\~ao Henriques}
	{}
	{SIGBOVIK_2017_paper_13}
	{1cm}
	{}

@@

\addtrack{Groundhog track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{1cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad and\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{3cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{3cm}
	{}
\addreview{SIGBOVIK_2017_review-23}{0cm}
